The Globular Cluster System of the Auriga Simulations

### 2019-03-26 AurigaGCS.tex
Implemented Sec. 4.1 Results / Metallicity distribution

\subsection{Total GC mass in metallicity-radial space}
\label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the 
MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. Both
quantities are readily available in H96e10, but the galactocentric radius
of GCs in M31 is not available in CR16. Therefore we follow 
\citet[][Sec.~4.1]{2019arXiv190111229W} to calculate the projected radius 
$R_{\text{proj}}$ from the observed positions, adopting M31's central position
from the NASA Extragalactic Database\footnote{\url{https://ned.ipac.caltech.edu/}} 
$(\alpha_0, \, \delta_0) = 
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$ 
and distance $D_{\text{M31}} = 778$~kpc (McConnachie et al. 2005; Conn  et  al. 2012).
We calculate $R_{\text{GC}}$ as `average deprojected distance`
$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$.
We compare these observations to the Auriga simulations later on in 
Section~\ref{sec:discussion_FeHRgc},

@@

We consider the metallicity distribution in Sec.~\ref{sec:results_FeH} 
the distribution of galactocentric radii in Sec.~\ref{sec:results_Rgc}, and the
combination of both in Sec.~\ref{sec:FeHRgc}.

@@

Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the
[Fe/H] distribution of star particles in the Auriga simulations. The mean
metallicity of old star particles lies in the range $-1.0$ to $-0.5$ and the
dispersion increases with decreasing metallicity. For comparison, the mean
of all star particles populates the range $-0.25$ to $0$ with a near-constant
dispersion a bit above $0.5$. Old accreted stars in the Auriga haloes reach
mean metallicities between $-1.5$ and $-1.0$, which is considerably lower than 
the old- and old insitu populations. Most Auriga L4 haloes have old insitu 
populations with mean metallicities around $-0.5$. The old accreted populations 
follow the trent of increasing dispersion with decreasing mean metallicity, but 
notably the old insitu populations all have a constant dispersion of roughly
$0.45$. We show the values calculated using all MW (M31) GCs in purple (magenta),
and literature values of the metal-rich (metal-poor) component of the MW GCS
as black solid (open) dots.

Figure~\ref{fig:FeH} shows the mass-weighted metallicity distribution of the
Auriga L4 haloes. Lines show the median value and the shaded regions indicate 
the $1\sigma$ interval (i.e. scatter between runs with different initial 
conditions which thus have unique merger histories). We notice once more that
the peak metallicity shifts from $0$ to $-0.5$ for old stars (orange solid)
compared to all stars (orange dotted).
(orange solid), \emph{old in-situ} stars (blue solid), and \emph{old accreted} stars
(red solid). 
of \emph{all stars} (orange dotted),

The MW (M31) GCS is shown in purple (magenta). We use the 
same bin sizes for the simulations as for the observations, explicitly shown for
the observed profiles.

@@

The peak of the distribution shifts down from [Fe/H] $\thicksim 0.0$ to 
$\thicksim -0.6$ for the \emph{old stars} compared to \emph{all stars} while the 
mass at the peak lowers by roughly one dex. Moreover, we find that the 
metallicity range $-3 <$ [Fe/H] $< -1$ is only populated by the GC candidates, 
while [Fe/H] $> -1$ is dominated by star particles younger than 10~Gyr.
Furthermore, the \emph{old accreted} sub set contributes most significantly to 
the range $-3 <$ [Fe/H] $< -1$, and the contribution of the \emph{old in-situ}
stars at these metallicities declines steeper with declining metallicity 
than the \emph{old accreted} population. We note that the scatter between different
Auriga haloes is much smaller than the difference between the MW and M31 GCSs.
We conclude that old star particles in the Auriga simulation suite as a whole 
cannot be consistent with both the Milky Way and the Andromeda globular cluster
system.

The middle (bottom) panel shows the ratio of the simulated mass to the mass in
the MW (M31) GCS. We observe an increasing trend with increasing metallicity 
for the Milky Way over the entire range of the data, while the M31 GCS shows
this increase only in the range [Fe/H]$>$-0.5 (although not for the \emph{old
accreted} component.

@@

@@

\subsection{Metallicity-radial space}
\label{sec:discussion_FeHRgc}
See Figure~\ref{fig:observations_FeHRgc} in Section~\ref{sec:observations_FeHRgc}.

@@

\subsection{From star particles to globular clusters}
\label{sec:star-to-gc}
Star particles are not globular clusters. Many stars do form in clusters, but
not all clusters end up gravitationally bound. Star particles in the
Auriga simulations represent single-age stellar populations that have formed
at the same location within the galaxy. Therefore one could assume a model
for the star cluster formation efficiency $\Gamma$, which could be used to 
`convert' star particles to bound star clusters e.g. Kruijssen (2012). This 
model relies on the local birth properties of the star particles. However, 
in our analysis we can retrieve the properties of the star particle in the 
first snapshot it was recorded, but not the gas properties at times of birth.
Therefore we are unable to model the formation of star clusters in more detail.

>>>>

\subsection{Total GC mass in metallicity-radial space}
\label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. Both
quantities are readily available in H96e10, but the galactocentric radius
of GCs in M31 is not available in CR16. Therefore we follow
\citet[][Sec.~4.1]{2019arXiv190111229W} to calculate the projected radius
$R_{\text{proj}}$ from the observed positions, adopting M31's central position
from the NASA Extragalactic Database\footnote{\url{https://ned.ipac.caltech.edu/}}
$(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 778$~kpc (McConnachie et al. 2005; Conn  et  al. 2012).
We calculate $R_{\text{GC}}$ as `average deprojected distance`
$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$.
We compare these observations to the Auriga simulations later on in
Sec.~\ref{sec:discussion_FeHRgc},

@@

We consider the metallicity distribution in Sec.~\ref{sec:results_FeH}
the distribution of galactocentric radii in Sec.~\ref{sec:results_Rgc}, and the
combination of both in Sec.~\ref{sec:results_FeHRgc}.

@@

Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the
[Fe/H] distribution of star particles in the Auriga simulations. The mean
metallicity of old star particles lies in the range $-1.0$ to $-0.5$ and the
dispersion increases with decreasing metallicity. For comparison, the mean
of all star particles populates the range $-0.25$ to $0$ with a near-constant
dispersion a bit above $0.5$. Old accreted stars in the Auriga haloes reach
mean metallicities between $-1.5$ and $-1.0$, which is considerably lower than
the old- and old insitu populations. Most Auriga L4 haloes have old insitu
populations with mean metallicities around $-0.5$. The old accreted populations
follow the trent of increasing dispersion with decreasing mean metallicity, but
notably the old insitu populations all have a constant dispersion of roughly
$0.45$. We show the values calculated using all MW (M31) GCs in purple (magenta),
and literature values of the metal-rich (metal-poor) component of the MW GCS
as black solid (open) dots. We further discuss the comparison between the
simulations and the observations in Sec.~\ref{sec:discussion_FeH}

Figure~\ref{fig:FeH} shows the mass-weighted metallicity distribution of the
Auriga L4 haloes. Lines show the median value and the shaded regions indicate
the $1\sigma$ interval around it (i.e. scatter between runs with different initial
conditions which thus have unique merger histories). We notice again that
the peak metallicity shifts down from $0$ to $-0.5$ for old stars (orange solid)
compared to all stars (orange dotted) while the mass at the peak lowers by 
roughly one dex. The mass budget of the old stars is
dominated by the old insitu population (blue solid) below [Fe/H]=$-1$, and by
the old accreted stars (red solid) above this value. We show the MW (M31) GCS 
in purple (magenta) and we show the ratio of the simulated to the observed 
profiles in the middle (bottom) panel. This mass excess can be thought of as a
combination of the bound cluster formation efficiency and disruptive processes,
further discussed in Sec.~\ref{sec:discussion_mass_excess}.

@@

@@

Furthermore, 
We note that the scatter between different
Auriga haloes is much smaller than the difference between the MW and M31 GCSs.
We conclude that old star particles in the Auriga simulation suite as a whole
cannot be consistent with both the Milky Way and the Andromeda globular cluster
system.

We observe an increasing trend with increasing metallicity
for the Milky Way over the entire range of the data, while the M31 GCS shows
this increase only in the range [Fe/H]$>$-0.5 (although not for the \emph{old
accreted} component.

@@

\subsection{Metallicity-radial space}
\label{sec:discussion_FeHRgc}
See Figure~\ref{fig:observations_FeHRgc} in Sec.~\ref{sec:observations_FeHRgc}.

@@

\subsection{From star particles to globular clusters}
\label{sec:discussion_mass_excess}
Star particles are not globular clusters. Many stars do form in clusters, but
not all clusters end up gravitationally bound. Star particles in the
Auriga simulations represent single-age stellar populations that have formed
at the same location within the galaxy. Therefore one could assume a model
for the star cluster formation efficiency $\Gamma$, which could be used to
`convert' star particles to bound star clusters e.g. Kruijssen (2012). This
model relies on the local birth properties of the star particles. However,
in our analysis we can retrieve the properties of the star particle in the
first snapshot it was recorded, but not the gas properties at times of birth.
Therefore we are unable to model the formation of star clusters in more detail.
